Figure Extra

### 2022-07-15 Figures/Figures_nonTCGA.Rmd
add Thomas benchmark

################################################################################
benchmark_corrplots <- function(deconv_data, true_estimates, key, title){
  # build the data
  true_subset_ <- true_estimates %>%  na.exclude() %>%
    arrange(factor(get(key), levels = get(key)))

@@

  deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = signature_dict, key = key)
  identical(true_subset[[key]], deconv_subset_summary[[key]]) %>% stopifnot()

@@

# GSE72056
## Data loading
```{r}
deconv <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/Projects/CRCT/21 - Epigenomics and network modelling of heterogeneity in immuno-oncology/Ting Xie/2021/CIBERSORTx/final_example_signatures/all_deconvolutions/all_deconvolutions_Melanoma_GSE72056_no_malighant.txt") %>% dplyr::rename_with(~str_replace(.,"__", "_CBSX_"))  %>% dplyr::rename_with(~str_replace(.,"__", "_")) #! fix naming of deconv results

ground_truth <- read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Facs_Melanoma_GSE72056.txt") %>% as_tibble(rownames = "Samples")

@@

```{r}
# Lists of celltypes of each signature
## signature dictionary construction (can use . as regexp!)
## uncoment print of functions to check that you detect what you want.
## non matching signatures/methods (all 0) are removed.
signature_dict <- list()
signature_dict[["BPRNACan"]] <- list(B = c("B"),
                                     CAFs = c(),
                                     CD4 = c("CD4"),
                                     CD8 = c("CD8"),
                                     Endothelial = c(),
                                     Macrophages = c("M0", "M1", "M2"),
                                     NK = c("NK"),
                                     Th = c(),
                                     Treg = c(),
                                     Cancer = c("cancer"),
                                     Other = c("Mono", "Neu"))

signature_dict[["BPRNACanProMet"]] <- signature_dict[["BPRNACan"]]
signature_dict[["BPRNACan3DProMet"]] <- signature_dict[["BPRNACan"]]

signature_dict[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(B = c("B.cells"),
                                     CAFs = c(),
                                     CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     Endothelial = c(),
                                     Macrophages = c(),
                                     NK = c("NK.cells"),
                                     Th = c(),
                                     Treg = c(),
                                     Cancer = c(),
                                     Other = c("Monocytes","NKT.cells"))

signature_dict[["CBSX_LM22"]] <- list(B = c("B.cells.naive", "B.cells.memory", "Plasma.cells"),
                                     CAFs = c(),
                                     CD4 = c("T.cells.CD4.naive", "T.cells.CD4.memory.resting", "T.cells.CD4.memory.activated"),
                                     CD8 = c("T.cells.CD8"),
                                     Endothelial = c(),
                                     Macrophages = c("Macrophages.M0", "Macrophages.M1", "Macrophages.M2"),
                                     NK = c("NK.cells.resting", "NK.cells.activated"),
                                     Th = c("T.cells.follicular.helper", "T.cells.gamma.delta"),
                                     Treg = c("T.cells.regulatory..Tregs."),
                                     Cancer = c(),
                                     Other = c("Monocytes", "Dendritic.cells.resting", "Dendritic.cells.activated", "Mast.cells.resting", "Mast.cells.activated", "Eosinophils", "Neutrophils"))

signature_dict[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(B = c("B.cells"),
                                     CAFs = c("CAF"),
                                     CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     Endothelial = c("Endothelial.cells"),
                                     Macrophages = c("Macrophages"),
                                     NK = c("NK.cells"),
                                     Th = c(),
                                     Treg = c(),
                                     Cancer = c("Malignant"),
                                     Other = c())

signature_dict[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(B = c("B.cells"),
                                     CAFs = c("CAFs"),
                                     CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     Endothelial = c("Endothelial.cells"),
                                     Macrophages = c("Macrophages"),
                                     NK = c(),
                                     Th = c(),
                                     Treg = c(),
                                     Cancer = c("Malignant.cells"),
                                     Other = c("Dendritic.cells", "Mast.cells", "Myocytes"))

signature_dict[["Quantiseq"]] <- list(B = c("B.cell"),
                                     CAFs = c(),
                                     CD4 = c("T.cell.CD4+.(non-regulatory)"),
                                     CD8 = c("T.cell.CD8+"),
                                     Endothelial = c(),
                                     Macrophages = c("Macrophage.M1", "Macrophage.M2"),
                                     NK = c("NK.cell"),
                                     Th = c(),
                                     Treg = c("T.cell.regulatory(Tregs)"),
                                     Cancer = c(),
                                     Other = c("Monocyte", "Neutrophil", "Myeloid.dendritic.cell", "uncharacterized.cell"))

# signature_dict[["CCLE_TIL10"]] <- list(B = c(),
#                                      CAFs = c(),
#                                      CD4 = c(),
#                                      CD8 = c(),
#                                      Endothelial = c(),
#                                      Macrophages = c(),
#                                      NK = c(),
#                                      Th = c(),
#                                      Treg = c(),
#                                      Cancer = c(),
#                                      Other = c())

# signature_dict[[""]] <- list(B = c(),
#                                      CAFs = c(),
#                                      CD4 = c(),
#                                      CD8 = c(),
#                                      Endothelial = c(),
#                                      Macrophages = c(),
#                                      NK = c(),
#                                      Th = c(),
#                                      Treg = c(),
#                                      Cancer = c(),
#                                      Other = c())

@@

```{r}
benchmark_corrplots(deconv_data = deconv, true_estimates = ground_truth,  key = "Samples", title = "GSE72056")
# corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
# corrplots$Neutrophils <- corrplots$Neutrophils + rremove("y.text")
# summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")
# 
# ggsave("Fig2_summary_corrplot.pdf", dpi = "print", width = 250, height = 100, units = "mm", scale = 2.5)
```

>>>>

################################################################################
benchmark_corrplots <- function(deconv_data, true_estimates, dict, key, title){
  # build the data
  true_subset_ <- true_estimates %>%  na.exclude() %>%
    arrange(factor(get(key), levels = get(key)))

@@

  deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = dict, key = key)
  identical(true_subset[[key]], deconv_subset_summary[[key]]) %>% stopifnot()

@@

# GSE72056
## Data loading
```{r}
deconv_GSE72056 <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/Projects/CRCT/21 - Epigenomics and network modelling of heterogeneity in immuno-oncology/Ting Xie/2021/CIBERSORTx/final_example_signatures/all_deconvolutions/all_deconvolutions_Melanoma_GSE72056_no_malighant.txt") %>% dplyr::rename_with(~str_replace(.,"__", "_CBSX_"))  %>% dplyr::rename_with(~str_replace(.,"__", "_")) #! fix naming of deconv results

truth_GSE72056 <- read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Facs_Melanoma_GSE72056.txt") %>% as_tibble(rownames = "Samples")

@@

```{r}
# Lists of celltypes of each signature
## signature dictionary construction (can use . as regexp!)
## uncoment print of functions to check that you detect what you want.
## non matching signatures/methods (all 0) are removed.
dict_GSE72056 <- list()
dict_GSE72056[["BPRNACan"]] <- list(B = c("B"),
                                     CAFs = c(),
                                     CD4 = c("CD4"),
                                     CD8 = c("CD8"),
                                     Endothelial = c(),
                                     Macrophages = c("M0", "M1", "M2"),
                                     NK = c("NK"),
                                     Th = c(),
                                     Treg = c(),
                                     Cancer = c("cancer"),
                                     Other = c("Mono", "Neu"))

dict_GSE72056[["BPRNACanProMet"]] <- dict_GSE72056[["BPRNACan"]]
dict_GSE72056[["BPRNACan3DProMet"]] <- dict_GSE72056[["BPRNACan"]]

dict_GSE72056[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(B = c("B.cells"),
                                     CAFs = c(),
                                     CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     Endothelial = c(),
                                     Macrophages = c(),
                                     NK = c("NK.cells"),
                                     Th = c(),
                                     Treg = c(),
                                     Cancer = c(),
                                     Other = c("Monocytes","NKT.cells"))

dict_GSE72056[["CBSX_LM22"]] <- list(B = c("B.cells.naive", "B.cells.memory", "Plasma.cells"),
                                     CAFs = c(),
                                     CD4 = c("T.cells.CD4.naive", "T.cells.CD4.memory.resting", "T.cells.CD4.memory.activated"),
                                     CD8 = c("T.cells.CD8"),
                                     Endothelial = c(),
                                     Macrophages = c("Macrophages.M0", "Macrophages.M1", "Macrophages.M2"),
                                     NK = c("NK.cells.resting", "NK.cells.activated"),
                                     Th = c("T.cells.follicular.helper", "T.cells.gamma.delta"),
                                     Treg = c("T.cells.regulatory..Tregs."),
                                     Cancer = c(),
                                     Other = c("Monocytes", "Dendritic.cells.resting", "Dendritic.cells.activated", "Mast.cells.resting", "Mast.cells.activated", "Eosinophils", "Neutrophils"))

dict_GSE72056[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(B = c("B.cells"),
                                     CAFs = c("CAF"),
                                     CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     Endothelial = c("Endothelial.cells"),
                                     Macrophages = c("Macrophages"),
                                     NK = c("NK.cells"),
                                     Th = c(),
                                     Treg = c(),
                                     Cancer = c("Malignant"),
                                     Other = c())

dict_GSE72056[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(B = c("B.cells"),
                                     CAFs = c("CAFs"),
                                     CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     Endothelial = c("Endothelial.cells"),
                                     Macrophages = c("Macrophages"),
                                     NK = c(),
                                     Th = c(),
                                     Treg = c(),
                                     Cancer = c("Malignant.cells"),
                                     Other = c("Dendritic.cells", "Mast.cells", "Myocytes"))

dict_GSE72056[["Quantiseq"]] <- list(B = c("B.cell"),
                                     CAFs = c(),
                                     CD4 = c("T.cell.CD4+.(non-regulatory)"),
                                     CD8 = c("T.cell.CD8+"),
                                     Endothelial = c(),
                                     Macrophages = c("Macrophage.M1", "Macrophage.M2"),
                                     NK = c("NK.cell"),
                                     Th = c(),
                                     Treg = c("T.cell.regulatory(Tregs)"),
                                     Cancer = c(),
                                     Other = c("Monocyte", "Neutrophil", "Myeloid.dendritic.cell", "uncharacterized.cell"))

# dict_GSE72056[["CCLE_TIL10"]] <- list(B = c(),
#                                      CAFs = c(),
#                                      CD4 = c(),
#                                      CD8 = c(),
#                                      Endothelial = c(),
#                                      Macrophages = c(),
#                                      NK = c(),
#                                      Th = c(),
#                                      Treg = c(),
#                                      Cancer = c(),
#                                      Other = c())

# dict_GSE72056[[""]] <- list(B = c(),
#                                      CAFs = c(),
#                                      CD4 = c(),
#                                      CD8 = c(),
#                                      Endothelial = c(),
#                                      Macrophages = c(),
#                                      NK = c(),
#                                      Th = c(),
#                                      Treg = c(),
#                                      Cancer = c(),
#                                      Other = c())

@@

```{r}
benchmark_corrplots(deconv_data = deconv_GSE72056, true_estimates = truth_GSE72056, dict = dict_GSE72056, key = "Samples", title = "GSE72056")
# corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
# corrplots$Neutrophils <- corrplots$Neutrophils + rremove("y.text")
# summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")
# 
# ggsave("Fig2_summary_corrplot.pdf", dpi = "print", width = 250, height = 100, units = "mm", scale = 2.5)
```

# Thomas RNAseq #! Change name!
## Data loading
```{r}
deconv_Thomas <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/Projects/CRCT/21 - Epigenomics and network modelling of heterogeneity in immuno-oncology/Ting Xie/2021/CIBERSORTx/final_example_signatures/all_deconvolutions/all_deconvolutions_Thomas_RNAseq_part.txt") %>%
  dplyr::rename_with(~str_replace(.,"__", "_CBSX_")) %>%
  dplyr::rename_with(~str_replace(.,"__", "_"))#! fix naming of deconv results

load( "/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meyloma_ludo/meyloma.RData")
truth_Thomas <- as_tibble(FACS_Thomas_mean, rownames = "Samples") %>%  mutate(Samples = as.numeric(Samples))

```{r}
# Lists of celltypes of each signature
## signature dictionary construction (can use . as regexp!)
## uncoment print of functions to check that you detect what you want.
## non matching signatures/methods (all 0) are removed.
dict_Thomas <- list()
dict_Thomas[["BPRNACan"]] <- list(CD4 = c("CD4"),
                                     CD8 = c("CD8"),
                                     NK = c("NK"))

dict_Thomas[["BPRNACanProMet"]] <- dict_Thomas[["BPRNACan"]]
dict_Thomas[["BPRNACan3DProMet"]] <- dict_Thomas[["BPRNACan"]]

dict_Thomas[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     NK = c("NK.cells"), #"NKT.cells"?
                                     )

dict_Thomas[["CBSX_LM22"]] <- list(CD4 = c("T.cells.CD4.naive", "T.cells.CD4.memory.resting", "T.cells.CD4.memory.activated"), # "T.cells.follicular.helper", "T.cells.gamma.delta", "T.cells.regulatory..Tregs."?
                                     CD8 = c("T.cells.CD8"),
                                     NK = c("NK.cells.resting", "NK.cells.activated"))

dict_Thomas[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     NK = c("NK.cells"))

dict_Thomas[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     NK = c())

dict_Thomas[["Quantiseq"]] <- list(CD4 = c("T.cell.CD4+.(non-regulatory)"), # "T.cell.regulatory(Tregs)"
                                   CD8 = c("T.cell.CD8+"),
                                   NK = c("NK.cell"))

```{r}
benchmark_corrplots(deconv_data = deconv_Thomas, true_estimates = truth_Thomas, dict = dict_Thomas,  key = "Samples", title = "Thomas")
# corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
# corrplots$Neutrophils <- corrplots$Neutrophils + rremove("y.text")
# summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")
# 
# ggsave("Fig2_summary_corrplot.pdf", dpi = "print", width = 250, height = 100, units = "mm", scale = 2.5)
```
